More than study on Supersymmetry this PhD was my research for my adult life. I am proud of myself that I went over this very important chapter of my life. Many are the people that I met along the way during those years and several are the ones that I have to thank. \\


Thanks to Christian for his constant supervising, for the several lectures you gave until the end and for the music advices.\\

Thanks to Peter that took over the supervising in the last year of the thesis path.\\

Thanks to the members of the Committee that joined in the day of my Disputation.\\

Thanks to Jori and Benedict not only for being incredible friends but also for giving hospitality when I didn't have nowhere to go. To you two guys I owe you a bit on peace of mind during the summer-winter 2017. And thanks for all the advices you gave over the final steps of the thesis, also the legal ones.\\

Thanks to Simon, Marek and Lara for being the best adventure-misadventure partners of my last years. Thanks also to Anka and Ola for being the sidekicks of those amazing experiences. Many are the things we did and I will treasure each one of them.\\

Thanks to Sonja for all the time spent together. Thanks again for taking my defenses when injustice knocked at the door. And thanks one more time for the hospitality anytime I needed.\\

Thanks to the rest of the gang Pascal, Anne, Manu, Steffen, Franzi, Jacek, Tini, Daniel and Sasha. I owe you the best nights of the last year. I hope our friendship will grow stronger than ever.\\

Thanks to Steffi for our time in the name of lightness.\\

Thanks to Lumen for being the light beacon towards positiveness.\\

Thanks to Erk and Eva for their friendship, born in an unconventional way and steadily growing.\\

Thanks to the Hoffmann and Vanelderen family. You all belong to a big chunk of my heart.\\

Thanks to Adrian, Sam, Paolo for the preparation in the last steps of the PhD. \\

Thanks to my clan of gamers and long term friends, Ciucciamerlazzi. I wish us ten thousand years of silliness, irreverent talks, meaningless online battles and laughs.\\

Thanks to Jenni for the peace of mind, love and support she showed me during this last period. Blessed is the day we met.\\

A special thanks goes to my entire big family. I could not have not done any of this without your support, love, emergency parachutes, advices and countless moments together. I never felt far from all of you even though we are not living anymore in the same country. Forever yours.\\


