The Standard Model of particle physics synthesize out current understanding of nature \cite{Spiesberger:2000ks}. This model managed over the decades to predict and lead to the discovery of several elementary particles thanks to the conjoint effort of the experimental and theoretical scientific community. 

Even after the many successful discoveries, ending with the Higgs Boson discovered in 2012 at the Large Hadron Collider \cite{Aad:2012tfa,Chatrchyan:2012xdj}, the Standard Model is not considered the final theory of particle physics. First of all, the theory is not complete. for example, it incorporates neither general relativity nor neutrino oscillations and does not provide a dark matter candidate. Furthermore, the Standard Model suffers from at least two fine tuning problems: the hierarchy problem and the strong CP problem. Although these problems are not actual inconsistencies, many physicists argue that they hint to physics beyond the Standard Model. As final reason the Higgs boson mass, measured at a value of around 125\gev, is considered very low regarding the huge radiative corrections at the Planck scale ($\approx 10^{19}\gev$). All these defects and tensions motivate both theoretical and experimental physicists to formulate theories beyond the Standard Model. One model in particular tries to solve the above mentioned problems through a new symmetry into the Lagrangian formulation of particle physics, a so-called supersymmetry (SUSY). This symmetry relates bosons and fermions by new fermionic generators and leads to the prediction of a supersymmetric partner particle for each of the particles contained in the Standard Model, leading to very drastic phenomenological implications. As direct consequence a very large number of searches has been performed over the last decays in many high energy physics experiment. 

With the successful operation of the Large Hadron Colliders, numerous results placing constraints on extensions to the standard model (SM) have been presented by the ATLAS and CMS experiments. In particular, in SUSY models, limits in excess of 1\tev have been placed on the masses of the strongly produced gluinos and first- and second generation squarks. In contrast, mass limits on the weakly produced charginos (\charginopm) and neutralinos (\neutralinotwo), with much smaller production cross sections, are much less severe. The limits for charginos and neutralinos are especially weak in so-called compressed-mass- spectrum scenarios, in which the mass of the lightest supersymmetric particle (LSP) is only slightly less than the masses of other SUSY states. The chargino-neutralino sector plays a crucial role in the connection between dark matter and SUSY: in SUSY models with R-parity conservation, the lightest neutralino \neutralinoone often takes the role of the LSP and is a dark matter candidate. Several searches on the chargino/neutralino system have been performed and showed a limited sensitivity in case the \charginopm and \neutralinotwo are nearly mass degenerate. Electroweak SUSY particles can be also produced in pairs along with two jets in in pure electroweak processes through vector-boson-fusion. This topology is characterized by the presence of two forward jets, in opposite hemispheres o fthe detector, leading to a large dijet invariant mass (\mjj). A search in the VBF topology offers a new and complementary means to directly probe the electroweak sector of SUSY, especially in compressed-mass-spectrum scenarios 

After an introduction to the theoretical and experimental background, this PhD thesis presents two different studies. The first part consist in a search for supersymmetric particles in 19.7 \invfb of data, taken in the year 2012 at 8\tev of center-of-mass energy at the CMS detector. The second part shows a sensitivity and limit setting study performed with 85 \invfb of simulated data at 13\tev.
